A Dependently Typed Multi-Stage Calculus

### 2019-08-23 text/informal-overview.tex
Fix an imcomplete sentence.

At first, the restriction above sounds too severe, because a term like
\(\lambda x:\I. \TB_\alpha (\lambda y:\text{Vector }x.M) \), which
models a typical code generator which takes the size $x$ and returns
code for vector manipulation specialized to the given size.  It seems
crucial for \(y\) to be given a type indexed by $x$.  We can address
this problem by CSP---In fact,
$\text{Vector }x$ is not well formed at $\alpha$ under $x:\I@\varepsilon$
but $\text{Vector }(\%_\alpha x)$ is!  So, we can still write
\(\lambda x:\I. \TB_\alpha (\lambda y:\text{Vector }(\%_\alpha x).M) \)
for the typical sort of code generators.

>>>>

At first, the restriction above sounds too severe, because a term like
\(\lambda x:\I. \TB_\alpha (\lambda y:\text{Vector }x.M) \), which models a
typical code generator which takes the size $x$ and returns code for vector
manipulation specialized to the given size, frequently appears. It seems crucial
for \(y\) to be given a type indexed by $x$. We can address this problem by
CSP---In fact, $\text{Vector }x$ is not well formed at $\alpha$ under
$x:\I@\varepsilon$ but $\text{Vector }(\%_\alpha x)$ is! So, we can still
write \(\lambda x:\I. \TB_\alpha (\lambda y:\text{Vector }(\%_\alpha x).M) \)
for the typical sort of code generators.
